Summary of correctness of 220 (from 44 original ones) causal sentences analyzed by GPT4

12 wrongs in file: meaning 42 sentences non-causal or with cause/effect inverted. (19\% errors)


1.
5.
Sentence: Regular maintenance prevents breakdowns in machinery.
   - Cause: Regular maintenance
   - Trigger: prevents
   - Effect: breakdowns in machinery
   
   
2.
15. ******WRONG!
Sentence: The speaker of Parliament read a roll call of the 275 elected members with a goal of shaming the no-shows.
Cause: shaming no-shows
Trigger: with a goal
Effect: a roll call of the 275 elected members

Machine Generation: 
1. The teacher assigned extra homework with a goal of reinforcing the day's lessons.
   - Cause: reinforcing the day's lessons
   - Trigger: with a goal
   - Effect: assigning extra homework

2. The city council implemented stricter parking regulations with a goal of reducing traffic congestion.
   - Cause: reducing traffic congestion
   - Trigger: with a goal
   - Effect: stricter parking regulations

3. The company introduced flexible working hours with a goal of increasing employee satisfaction.
   - Cause: increasing employee satisfaction
   - Trigger: with a goal
   - Effect: flexible working hours

4. The coach increased the intensity of the training sessions with a goal of improving the team's performance.
   - Cause: improving the team's performance
   - Trigger: with a goal
   - Effect: increased intensity of training sessions

5. The government launched a public health campaign with a goal of raising awareness about the importance of vaccinations.
   - Cause: raising awareness about the importance of vaccinations
   - Trigger: with a goal
   - Effect: launching a public health campaign
-------------------------------------------------
3.
16.
Sentence: The speaker of Parliament read a roll call of the 275 elected members with the objective of shaming the no-shows.
Cause: shaming no-shows
Trigger: with the objective
Effect: a roll call of the 275 elected memebers
wrong!!!
Machine Generation: 
1. The chef prepared a sumptuous five-course meal with the intention of impressing the food critics.
   - Cause: impressing food critics
   - Trigger: with the intention
   - Effect: preparing a sumptuous five-course meal

2. The company launched an aggressive social media campaign with the goal of increasing their brand awareness among young adults.
   - Cause: increasing brand awareness among young adults
   - Trigger: with the goal
   - Effect: launching an aggressive social media campaign

3. The local council implemented a strict recycling program with the aim of reducing the community's carbon footprint.
   - Cause: reducing the community's carbon footprint
   - Trigger: with the aim
   - Effect: implementing a strict recycling program

4. The teacher assigned extra homework with the purpose of improving the students' understanding of the material.
   - Cause: improving students' understanding of the material
   - Trigger: with the purpose
   - Effect: assigning extra homework

5. The government introduced new tax incentives with the objective of encouraging small business growth.
   - Cause: encouraging small business growth
   - Trigger: with the objective
   - Effect: introducing new tax incentives
-------------------------------------------------
4.
23. WRONG!!!!
Sentence: The fox leapt in an attempt to catch the mouse.
Cause: catch the mouse
Trigger: an attempt to
Effect: the fox lept
Machine Generation: 
1. Cause: answer the phone  
   Trigger: in response to  
   Effect: the man hurried across the room  
   Sentence: The man hurried across the room in response to the ringing phone to answer it.

2. Cause: lose weight  
   Trigger: as a means to  
   Effect: she started jogging every morning  
   Sentence: She started jogging every morning as a means to lose weight.

3. Cause: quench his thirst  
   Trigger: in an attempt to  
   Effect: the traveler drank from the stream  
   Sentence: The traveler drank from the stream in an attempt to quench his thirst.

4. Cause: finish the project on time  
   Trigger: in order to  
   Effect: the team worked overtime  
   Sentence: The team worked overtime in order to finish the project on time.

5. Cause: impress the judges  
   Trigger: with the aim of  
   Effect: the chef carefully plated the dish  
   Sentence: The chef carefully plated the dish with the aim of impressing the judges.
   
-------------------------------------------------
5.
24. WRONG!!
Sentence: He kept his headphones on lest he disturb anyone.
Cause: he disturb anyone
Trigger: lest
Effect: kept headphones on
Machine Generation: 
1. She took an umbrella lest she get caught in the rain.
   - Cause: she get caught in the rain
   - Trigger: lest
   - Effect: took an umbrella

2. He spoke softly lest he wake the baby.
   - Cause: he wake the baby
   - Trigger: lest
   - Effect: spoke softly

3. They left early lest they miss their flight.
   - Cause: they miss their flight
   - Trigger: lest
   - Effect: left early

4. I saved my document frequently lest I lose any changes.
   - Cause: I lose any changes
   - Trigger: lest
   - Effect: saved my document frequently

5. She wore gloves lest her fingerprints be left behind.
   - Cause: her fingerprints be left behind
   - Trigger: lest
   - Effect: wore gloves
-------------------------------------------------

6.
25. WRONG!
Sentence: I left early in the hopes of beating the traffic.
Cause: the hopes of beating the traffic
Trigger: in the hopes of
Effect: left early
Machine Generation: 
1. Sentence: She studied hard throughout the semester with the intention of acing her finals.
   Cause: the intention of acing her finals
   Trigger: with the intention of
   Effect: studied hard throughout the semester

2. Sentence: He saved money diligently for years in order to buy his dream house.
   Cause: in order to buy his dream house
   Trigger: in order to
   Effect: saved money diligently for years

3. Sentence: She woke up at dawn aiming to witness the sunrise from the mountaintop.
   Cause: aiming to witness the sunrise from the mountaintop
   Trigger: aiming to
   Effect: woke up at dawn

4. Sentence: I drank plenty of water before the race in preparation for the intense heat.
   Cause: in preparation for the intense heat
   Trigger: in preparation for
   Effect: drank plenty of water before the race

5. Sentence: They planted trees around their house with the goal of creating more privacy.
   Cause: the goal of creating more privacy
   Trigger: with the goal of
   Effect: planted trees around their house
-------------------------------------------------

7.
26. wrong?
Sentence: He tricked me into coming with.
Cause: he tricked me
Trigger: into
Effect: coming with
Machine Generation: 
1. Sentence: The bright sunlight lured me outside.
   Cause: the bright sunlight
   Trigger: lured
   Effect: me going outside

2. Sentence: Her persuasion convinced me to join the club.
   Cause: her persuasion
   Trigger: convinced
   Effect: me joining the club

3. Sentence: The loud noise scared the birds away.
   Cause: the loud noise
   Trigger: scared
   Effect: the birds flying away

4. Sentence: His argument swayed my opinion on the matter.
   Cause: his argument
   Trigger: swayed
   Effect: my opinion changing

5. Sentence: The aroma enticed me into the bakery.
   Cause: the aroma
   Trigger: enticed
   Effect: me entering the bakery
-------------------------------------------------
8.
*******************WRONG!
3. Sentence: When the market opened, stock prices plummeted.
   - Cause: the market opened
   - Trigger: when
   - Effect: stock prices plummeted
*********************

9.
***************WRONG!
1. Sentence: Moments after stepping outside, she was soaked by the rain.
   Cause: stepping outside
   Trigger: moments after
   Effect: she was soaked by the rain
***********************

10.
41. WRONG!!!
Sentence: The investigation comes after government watchdogs raised red flags about classified material possibly being shared.
Cause: goverment watchdogs raised red flags about classified material possibly being shared
Trigger: after
Effect: the investigation

11.
************WRONG!
2. Sentence: Once the movie started, I realized I had seen it before.
   - Cause: the movie started
   - Trigger: once
   - Effect: I realized I had seen it before
*******************

12.
********WRONG?
5. Sentence: After reading the book, she felt inspired to write her own.
   - Cause: reading the book
   - Trigger: after
   - Effect: she felt inspired to write her own
-----------
